---
output:
  pdf_document:
    latex_engine: xelatex
header-includes:
    - \usepackage{fancyhdr}
    - \usepackage{fontspec}
    - \usepackage{xcolor}
    - \geometry{left = 0.5in,right = 0.5in}
mainfont: Roboto
sansfont: Roboto
urlcolor: purplepeopleeater
---
<!-- define color and adjust lengths for header and footer-->
\definecolor{purplepeopleeater}{RGB}{106,13,75}
\addtolength{\headheight}{3.0cm}
\addtolength{\topmargin}{-0.5in}
\addtolength{\footskip}{-0.225in}

<!-- % setup header -->
\pagestyle{fancy}
\fancyhf{}

<!-- header content -->
<!-- Uncomment the line of code below to include a header -->
\fancyhead[L]{\raisebox{-0.05\height}{\includegraphics[height = 2.5cm]{"/ma-DPH_logo.png"}}}
\fancyhead[R]{\Huge MASPHL Genomic Sequencing Run Report\\
\Large `r paste(Sys.Date())`}

<!-- create red header line -->
\renewcommand{\headrulewidth}{1pt}
\renewcommand{\headrule}{\hbox to\headwidth{%
    \color{purplepeopleeater}\leaders\hrule height \headrulewidth\hfill}}

<!-- footer content -->
\fancyfoot[C]{For research use only, not for clinical use.}
\fancyfoot[R]{\thepage}

<!-- create red footer line -->
\renewcommand{\footrulewidth}{1pt}
\renewcommand{\footrule}{\hbox to\headwidth{%
    \color{purplepeopleeater}\leaders\hrule height \headrulewidth\hfill}}

```{r include=FALSE}
## Libraries
library(knitr)
library(kableExtra)
## Figure size
# get date of report generation
date <- Sys.Date()
# set figure size
knitr::opts_chunk$set(out.width = "7.5in", out.height = "8in", fig.align = "left")
# set seed for reproducibility
set.seed(123)
```

The assembly of your sample genomes has been completed. Below are the sample IDs with corresponding metrics and pass/fail values.

## Sample Sequence Pass/Fail Status
```{r, table1, echo = FALSE}
# Separating out metrics file assembly info
columns <- c("coverage_after_trimming", "meanbaseq_trim", "meanmapq_trim", "assembly_status")
status_table$Sample_ID <- rownames(status_table)
consensus_metrics <- status_table[, c("Sample_ID", columns)]
colnames(consensus_metrics) <- c("Sample IDs", "Coverage", "Avg. Base Q", "Avg. Map Q", "Status")
rownames(consensus_metrics) <- NULL
kable(consensus_metrics, 'latex', booktabs = TRUE, linesep = '') %>%
  kable_styling(latex_options = c('striped', 'full_width'), font_size = 9)
```
